CO Interlopers Eloping from [C~\textsc{ii}] Surveys

### 2019-03-27 paper/ms.tex
Add SN macro
Add perfect auto-ps SNR
Add some more general formulae

\newcommand{\E}[1]{\mathrm{E}[#1]}
\newcommand{\Var}[1]{\mathrm{Var}[#1]}
\newcommand{\Cov}[2]{\mathrm{Cov}[#1,#2]}
\newcommand{\avg}[1]{\ensuremath{\langle #1 \rangle}}

@@

The Fisher matrix for our measurement is
\beq\label{eq:fisher}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
\eeq
where $l$, $l'$, $m$, and $m'$ sum over all lines being considered. Note that
we can make the substitution
\begin{equation*}
\sum_{\substack{l,l'\\l > l'}} \rightarrow 
\frac{1}{2} \sum_{\substack{l,l'\\l \neq l'}}\text{,}
\end{equation*}
without changing the value of the Fisher matrix. Thus it will sometimes be
easier to compute
\beq\label{eq:fisher4}
F_{i,j} = 
\frac{1}{4} \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
\eeq

@@

Consider the extremely trivial case such that $B_i = B$ and $N_i = N$ for all
lines $i$. In this case, if we have $n_l$ lines, the Fisher matrix reduces to
\beq\label{eq:fisher_supertrivial}
        F_{i,j} = V_k \frac{B^2}{N^2} \times
        \begin{cases}
             n_l-1 & \text{if $i=j$} \\
             1 &\text{if $i\neq j$} \\
        \end{cases}\text{.}
\eeq
In the large $n_l$ limit, the Fisher matrix becomes diagonal, and we can
therefore write the covariance matrix as
\beq\label{eq:cov_supertrivial_largen}
C_{i,j} = \frac{N^2}{V_k B^2} \frac{1}{n_l-1} \delta_{ij}\text{,}
\eeq
where $\delta_{ij}$ is the Kronecker delta. This leads us to the conclusion
that in the noise-dominated regime where each line has comparable
$\text{S}/\text{N}$, the constraining power on each line $i$ scales as
$1/n_l$. In other words, one can improve the constraint on $B_i$ without
executing additional observations of line $i$.

>>>>

\newcommand{\E}[1]{\mathrm{E}[#1]}
\newcommand{\Var}[1]{\mathrm{Var}[#1]}
\newcommand{\Cov}[2]{\mathrm{Cov}[#1,#2]}
\newcommand{\avg}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\SN}{\ensuremath{\text{S}/\text{N}}}

@@

The Fisher matrix for our measurement is
\beq\label{eq:fisher}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
\eeq
where $l$, $l'$, $m$, and $m'$ sum over all lines being considered. Note that
we can make the substitution
\begin{equation*}
\sum_{\substack{l,l'\\l > l'}} \rightarrow 
\frac{1}{2} \sum_{\substack{l,l'\\l \neq l'}}\text{,}
\end{equation*}
without changing the value of the Fisher matrix. Thus it will sometimes be
easier to compute
\beq\label{eq:fisher4}
F_{i,j} = 
\frac{1}{4} \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{.}
\eeq
We also note that a perfect auto-spectrum measurement will have a limit to the
precision of a $B_i$ as
\beq\label{eq:Bi_auto_snr}
\text{S}/\text{N}(B_i) = \frac{B_i^2}{\sqrt{N_i}}\sqrt{V_k}\text{.}
\eeq
This will be useful to compare to the $\text{S}/\text{N}$ we will compute for
the multi-field approach.

@@

Consider the extremely trivial case such that $B_i = B$ and $N_i = N$ for all
lines $i$. In this case, if we have $n_l$ lines, the Fisher matrix reduces to
\beq\label{eq:fisher_supertrivial}
        F_{i,j} = V_k \frac{B^2}{N^2} \times
        \begin{cases}
             n_l-1 & \text{if $i=j$} \\
             1 &\text{if $i\neq j$} \\
        \end{cases}\text{.}
\eeq
In the large $n_l$ limit, the Fisher matrix becomes diagonal, and we can
therefore write the covariance matrix as
\beq\label{eq:cov_supertrivial_largen}
C_{i,j} = \frac{N^2}{V_k B^2} \frac{1}{n_l-1} \delta_{ij}\text{,}
\eeq
where $\delta_{ij}$ is the Kronecker delta. This leads us to the conclusion
that in the noise-dominated regime where each line has comparable
\SN{}, then the \SN{} on the bias factor of each
line can be written as
\beq
\SN(B) =
\frac{B^2}{N} \sqrt{V_k(n_l-1)}
\eeq

Now let us consider a slightly more general case where $n_l \gg 1$ but we
allow each $B_i$ and $N_i$ to be any value, each of which has $B_i^2/N_i$ to
be of comparable value. In this case, we can approximate the Fisher matrix as
diagonal and write
\beq\label{eq:fisher_BiNi_samemag}
F_{i,j} = \frac{V_k}{N_i}\delta_{ij}
\sum_{\substack{l\neq i}}
\frac{B_l^2}{N_l}\text{.}
\eeq
Inversion of this matrix is trivial, and we can therefore write down the
$\text{S}/\text{N}$ on each bias factor as
\beq\label{eq:snr_nlgg1}
\text{S}/\text{N}(B_i) = \frac{B_i}{\sqrt{N_i}}
\sqrt{V_k} \left( \sum_{l\neq i} \frac{B_l^2}{N_l}\right)^{1/2}
\text{.}
\eeq
Now, suppose that of the lines $l\neq i$ one of them --- say, line $j$ --- is
measured to much higher precision than the other lines. Then the sum is
approximated by just the term with $l=j$, and we can approximate the \SN{}
{$\text{S}/\text{N}$} on $B_i$ as
\beq
\SN(B_i) \approx \frac{B_iB_j}{\sqrt{N_iN_j}}\sqrt{V_k}\text{.}
\eeq
Now, compare this to the \SN{} one would expect from the auto-spectrum:
\beq
\frac{\SN(B_i,\text{multi-field})}{\SN(B_i,\text{auto-spectrum})} =
\frac{B_j/\sqrt{N_j}}{B_i/\sqrt{N_i}}
\eeq
